Automated Verification Applied to Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-07-24 Tex/Old text/chapters/appendix.tex
thesis updated text

appendix appendix appendix appendix appendix appendix appendix appendix appendix appendix appendix appendix.

>>>>

%\textbf{List of Publications}
%
Here there are a list of papers that were written during the Thesis elaboration and the status of every submission until the date of this document.

\section{Journals}

Trindade, A., Cordeiro, L. \textbf{Automated Formal Verification of Stand-alone Solar Photovoltaic Systems}, submitted: 8-May-2019 , status: in review (2nr round, since 16-July-2019) by Elsevier Solar Energy (Impact Factor 4.374, CAPES A1 Interdisciplinary, CAPES A1 Engineering IV ) \url{https://www.journals.elsevier.com/solar-energy}

Trindade, A., Cordeiro, L. \textbf{An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative}, submitted: 29-June-2019, resubmitted: 09-July-2019, status: under review by Elsevier Applied Solar (Impact Factor 7.9, CAPES A1 Interdisciplinary, CAPES A2 Engineering IV, CAPES B1 Computer Science) \url{https://www.journals.elsevier.com/applied-energy}

\section{Congress}

Trindade, A., Cordeiro, L. \textbf{Automated Formal Synthesis of Optimal Sizing for Stand-Alone Solar Photovoltaic Systems}, submitted: 06-MAY-2019, status: under review by The IEEE/ACM Automated Software Engineering (ASE 2019) Conference (New Ideas Papers) \url{https://2019.ase-conferences.org/track/ase-2019-papers}

### 2019-07-24 Tex/Old text/chapters/chapter02.tex
thesis updated text

ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}. This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally. This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PV Systems Optimization Criteria}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}. This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally. This technique is called 'incremental SMT'~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PV Systems Optimization Criteria}
\label{sec:optcriteria}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-07-24 Tex/Old text/chapters/conclusion.tex
thesis updated text

It was described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques. It was considered five case studies from real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker). Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool. In particular, the proposed method was successful in finding sizing errors and indicating in details. Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the incremental configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than 2GB when compared to 9.2GB of CBMC and 19.2GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presenting in the field.
%New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study.

>>>>

It was described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques. It was considered five case studies from real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker). Although the verification method proposed takes longer than simulation methods, it is able to avoid the battery bank oversize produced by the simulation tool in houses $1$, $2$, $3$, and $4$. Moreover, it was not necessary to 'adapt' the tool, since the specialized simulation tool (HOMER Pro) had to be adjusted in order to not perform the optimization of the system. In addition, only the proposed method of automated verification was possible to validate a system with a specific battery autonomy, since HOMER Pro does not have this feature.

Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the 'incremental SMT' configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than $2$ GB when compared to $9.2$ GB of CBMC and 19.2GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presenting in the field.
%New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study.
